Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2024-05-13 manuscript/manuscript.tex
added link
changed readme
first thoughts

\presentaddress{21 Maxfelix Dr, Storrs, CT 06268}

@@

\abstract[Abstract]{The Kolmogorov--Smirnov (KS) test is a widely used statistical test that
assesses the conformity of a sample to a specified distribution. Its efficacy,
however, diminishes with serially dependent data and when parameters
within the hypothesized distribution are unknown. For independent data,
parametric and nonparametric bootstrap procedure are available to adjust for
estimated parameters. For serially dependent stationary data, parametric
bootstrap has been developed with a working serial dependence structure. A
counterpart for the nonparametric bootstrap approach, which needs a bias
correction, has not been studied. Addressing this gap, our study introduces a
bias correction method employing a nonparametric block bootstrap, which
approximates the distribution of the KS statistic accounting for unspecified
serial dependence and unspecified parameters. We assess its effectiveness
through simulations, scrutinizing both its size and power. The practicality of
our method is further illustrated with an examination of stock returns from the 
S\&P 500 index, showcasing its utility in real-world
applications.}

@@

First, let us review how the KS statistic is computed for an independent
sample with fitted parameters. Let $\hat\theta_n$ denote the parametrically
fitted parameters, which can be obtained from any consistent estimator with
asymptotic normality properties,  Let $F_n$ be the empirical distribution
function based on $X_1,...,X_n$.
Define 
\begin{equation*}
Y_n(x; \hat\theta_n) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n)).
\end{equation*}
Then, the one-sample KS goodness of fit statistic is 
\begin{equation*}
T_n := \sup_x|Y_n(x; \hat\theta_n)|.
\end{equation*}

@@

When $\{X_t: t = 1, \ldots, n\}$ are further serially dependent, the statistics
$T_n$ still provides a reasonable metric for deviation from the null
hypothesis. Nonetheless, the asymptotic distribution of $T_n$ cannot be fixed
even with the bias correction of \citet{babu2004goodness}, because the
correction requires independent sample.

@@

In summary, the procedure of the nonparametric bootstrap KS test for independent
sample is 
summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
\begin{enumerate}
\item
  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying basic bootstrap 
  on the original sample as
  defined previously.
\item
  Fit $F_\theta$ to $X^{(b)}_1,...,X^{(b)}_n$ and obtain estimate 
	$\hat\theta^{(b)}_n$ of $\theta$.
\item
  Obtain the empirical distribution function $F^{(b)}_n$ of
  $X^{(b)}_1,...,X^{(b)}_n$. 
\item
  Calculate bootstrap KS statistic
  \[
    T^{(b)}_n = \sup_x | \sqrt{n}\left(F^{(b)}_n(x) 
    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) |.
  \]
  where 
  $B_{n}(x) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is the known
  bias term.
\end{enumerate}

@@

@@

These distributions
were chosen to compare results on normal and non-normal
error structures. The specific parameters were chosen because the distributions 
are very similar and their
first two moments are the same. 
For the purposes of 
evaluating if the test holds it size, when $X_t \sim N(8, 8)$, we tested that the 
marginal distribution is from the
Normal family, or 
$X_t \sim N(\cdot \mid \mu, \sigma^2), \quad t = 1, \ldots, n$
for some unspecified $\mu$ and $\sigma$. When $X_t \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is from the Gamma family,
or
$X_t \sim \Gamma(\cdot \mid \alpha, \beta), \quad t = 1, \ldots, n$.
for some unspecified $\alpha$ and $\beta$.
For the block
bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
For each setting for $F$, $\tau$, and $n$, we replicate the method 1000 times 
to get the distribution of the p-values $p_r$
for the test when applied to samples from the same data generating process.

\begin{figure}[tbp]
  \centering
  \includegraphics[width = .9\textwidth]{figures/normal}
  \includegraphics[width = .9\textwidth]{figures/gamma}
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal normal distribution with true data generating distribution
    being $N(8,8)$ (upper) and marginal gamma distribution with true data
    generating distribution $\Gamma(8,1)$ (lower)}
  \label{fig:qq}
\end{figure}

Figure~\ref{fig:qq} shows the Quantile-Quantile (Q-Q)
plots of the p-values testing the marginal distribution of the stationary time
series generated from the null hypothesis, created with R packages
\textsl{qqplotr} and \textsl{ggplot2} \citep{qqplotr, ggplot2}. If the
distribution of the p-values is uniform, the points will be aligned with the
diagonal line. The plots suggest that the extent to which the p-values are
uniformly distributed is dependent on the sample size and the level of serial 
dependence.
A small sample size like $n = 100$ or $200$ seems adequate when Kendall's
$\tau$ is lower than 0.25. For Kendall's $\tau \geq 0.5$, a sample larger than
$n = 200$ seems necessary for the p-values to be normally distributed. For
Kendall's $\tau \geq 0.75$, a sample larger than $n = 800$ appears to be 
necessary, as the p-values are not aligned with the line in any of the Q-Q 
plots. This
is not necessarily a cause for concern, as (for normal margins)
a Kendall's $\tau$ corresponds to
a $\phi$ of 0.924, which is very high.
Additionally, positive serial dependence appears to misalign the distribution
of the p-values more so than negative serial dependences of the same strength.
Results are very similar for normal and gamma margins.

\begin{table}[tbp]
\centering
\caption{Rejection rates for test that sample follows its true
                    distribution family for
                   different values of AR(1) coefficient and for different 
                   significance levels.} 
\label{table:size}
\begin{tabular}{lllrrrrrrr}
  \toprule
$F(\cdot; \theta)$ & $n$ & $\alpha$ & $\tau = -0.75$ & $\tau = -0.5$ & $\tau = -0.25$ 
& $\tau = 0$ & $\tau = 0.25$ & $\tau = 0.5$ & $\tau = 0.75$ \\ 
  \midrule
{$N(8,8)$} & {100} & 0.01 & 0.052 & 0.013& 0.007 & 0.011 & 0.009 & 0.013 & 0.058 \\ 
& & 0.05 & 0.138 & 0.061 & 0.038 & 0.059 & 0.054 & 0.083 & 0.178 \\ 
& & 0.10 & 0.238 & 0.125 & 0.089 & 0.124 & 0.102 & 0.152 & 0.272 \\ 
& {200} & 0.01 & 0.043 & 0.009 & 0.006 & 0.017 & 0.011 & 0.018 & 0.062 \\ 
& & 0.05 & 0.130 & 0.058 & 0.041 & 0.051 & 0.053 & 0.061 & 0.175 \\ 
& & 0.10 & 0.202 & 0.120 & 0.101 & 0.107 & 0.110 & 0.125 & 0.266 \\ 
& {400} & 0.01 & 0.037 & 0.011 & 0.009 & 0.014 & 0.013 & 0.009 & 0.043 \\ 
& & 0.05 & 0.109 & 0.047 & 0.052 & 0.061 & 0.044 & 0.064 & 0.133 \\ 
& & 0.10 & 0.174 & 0.099 & 0.098 & 0.108 & 0.099 & 0.123 & 0.212 \\ 
& {800} & 0.01 & 0.023 & 0.011 & 0.008 & 0.011 & 0.011 & 0.011 & 0.038 \\ 
& & 0.05 & 0.088 & 0.043 & 0.040 & 0.055 & 0.042 & 0.053 & 0.125 \\ 
& & 0.10 & 0.166 & 0.097 & 0.095 & 0.102 & 0.107 & 0.109 & 0.196 \\ [1ex]
{$\Gamma(8,1)$} & {100} & 0.01 & 0.056 & 0.014 & 0.006 & 0.011 & 0.009 & 0.015 & 0.063 \\
  & & 0.05 & 0.144 & 0.063 & 0.037 & 0.059 & 0.053 & 0.083 & 0.180 \\ 
  & & 0.10 & 0.239 & 0.125 & 0.092 & 0.126 & 0.103 & 0.150 & 0.273 \\ 
  & {200} & 0.01 & 0.045 & 0.012 & 0.005 & 0.017 & 0.012 & 0.020 & 0.066 \\ 
  & & 0.05 & 0.127 & 0.058 & 0.045 & 0.052 & 0.054 & 0.056 & 0.173 \\ 
  & & 0.10 & 0.204 & 0.123 & 0.103 & 0.106 & 0.108 & 0.129 & 0.263 \\ 
  & {400} & 0.01 & 0.038 & 0.012 & 0.010 & 0.014 & 0.010 & 0.010 & 0.045 \\ 
  & & 0.05 & 0.106 & 0.049 & 0.051 & 0.062 & 0.042 & 0.063 & 0.128 \\ 
  & & 0.10 & 0.175 & 0.097 & 0.098 & 0.107 & 0.100 & 0.122 & 0.211 \\ 
  & {800} & 0.01 & 0.024 & 0.011 & 0.007 & 0.011 & 0.011 & 0.010 & 0.039 \\ 
  & & 0.05 & 0.089 & 0.043 & 0.041 & 0.055 & 0.044 & 0.051 & 0.121 \\ 
  & & 0.10 & 0.169 & 0.096 & 0.094 & 0.100 & 0.109 & 0.110 & 0.194 \\ 
   \bottomrule
\end{tabular}
\end{table}

For a closer scrutiny on whether the test holds its size at commonly used
significance levels 0.01, 0.05, and 0.10, Table~\ref{table:size}
summarizes the empirical sizes of the tests based on 1000 replicates.
The agreement between the empirical sizes and the nominal size
improves as sample size increases, as expected. For $\tau = -0.75$
and $\tau = 0.75$, a sample size as large as 800 is still not sufficient for the
agreemet to be reached. For weaker dependence levels, our approach is working
for $-0.25 < \tau < 0.25$ for $n = 100$. However, a larger sample size seems 
necessary, greater than 400 perhaps, for $\tau$ as strong as $0.5$. To 
summarize, for weaker dependence, our method works without need for a 
particularly large sample size, whereas for moderate dependence, a larger sample
size is required. For practical situations with a $\tau$ of magnitude 0.5 or
lower, it is still reasonable to recommend our method with $n \ge 400$.

\subsection{Power}
The power of the proposed test is investigated with data generated from
distributions that are not in the hypothesized distribution family. 
We generated the same scheme of time series as we did in the size investigation,
but tested that the time series was from the other distribution.
Because the support of $N(8, 8)$ is
$(-\infty, \infty)$, but the support of $\Gamma(8, 1)$ is $(0, \infty)$, we used
the \textsl{truncdist} package \citep{truncdist} to truncate the series at 
values less than or equal to 0 when testing that $N(8, 8)$ sample was
from $\Gamma(8, 1)$. For each setting for $F$, $\tau$, and $n$, we replicate the 
method $1000$ times 
to obtain a p-value $p_r$ for each $r \in \{1, \ldots, 1000\}$.
The empirical rejection rates were obtained at a nominal significance level 0.05.
Additionally, we constructed 95\% confidence intervals the actual rejection
rejection rate.

@@

Figure~\ref{fig:rr} displays the empirical power curve of the test at
significance level 0.05 as the lag-1 Kendall's~$\tau$ increases from
$-0.5$ to $0.5$. We omitted -0.75 and 0.75 from this study because we already 
found that our method doesn't work under the null hypothesis for such high
dependence levels. It appears that rejection rate seems to decline as $\tau$
increases. Rejection rates are negatively affected by positive serial 
dependence, but they do not seem to be affected by negative serial dependences
of the same strength.
Using $n \geq 400$ seems to be good enough
if $\tau < 0.5$, but using a $n \geq 800$ will result in 
rejection rates close to 1 for $0.5 < \tau < 0.5$.
Results for $n \geq 400$
do not appear to be to different when comparing gamma and normal 
margins, indicating that the method is robust to the marginal distribution.
The rejection rates for $n = 800$ are very 
high (almost 1), indicating that under $H_A$, the test is very powerful 
when a large enough sample size is used.

@@

Using the \textsl{tseries} package \citep{tseries}, 
we gathered daily closing prices for the S\&P 500 index from January 1st, 2020
to December 31st, 2023. Daily returns were obtained by taking the difference in
the logarithm of the closing prices. 
It is known as stylized facts that daily return series often exhibts nonlinear
dependence and unconditional heavy tails \citep[e.g.,][]{ryden1998stylized,
  cont2001empirical}. The lag-1 Kendall's $\tau$ of the series is
about $-0.0298$, indicating a fairly weak serial linear correlation, but
certainly not meaning absence of serial dependence.
Using our method, we tested that the daily returns are normally
distributed and Student's $t$ distributed 
with degrees of freedom $\nu \in \{30, 20, 10, 5, 4, 3, 2, 1\}$
with the proposed nonparametric block bootstrap (NPBB) method.
For comparison, we tested the same hypotheses using 1) the
semiparametric bootstrap (SPB) method of \citet{zeimbekakis2022misuses},
which accounts for both serial dependence and unspecified parameters;
2) nonparametric bootstrap (NPB) bias correction method of
\citet{babu2004goodness}; and and 3) the parametric bootstrap (PB) method shown
by \citet{zeimbekakis2022misuses}. The latter of the two methods discard the
serial dependence. In all methods, we used $B = 10,000$ bootstrap replicates.
The p-values for these tests are summarized in 
Table~\ref{table:SP5004}.

\begin{table}[ht]
\centering
\caption{P-values for 4 years of S\&P 500 stock return 
  data using different durations
  and different degrees of freedom for Student's $t$ distribution.
  NPBB: nonparametric block bootstrap;
  SPB: semiparametric bootstrap;
  NPB: nonparametric bootstrap;
  PB: parametric bootstrap.} 
\label{table:SP5004}
\begin{tabular}{ccccc}
  \toprule
$\nu$ & NPBB & SPB & NPB & PB\\ 
  \midrule
$\infty$ & 0.0001 & 0.0000 & 0.0000 & 0.0000 \\ 
  30 & 0.0019 & 0.0000 & 0.0000 & 0.0000 \\ 
  20 & 0.0027 & 0.0000 & 0.0000 & 0.0000 \\ 
  10 & 0.0125 & 0.0002 & 0.0003 & 0.0003 \\ 
  5 & 0.0610 & 0.0192 & 0.0222 & 0.0141 \\ 
  4 & 0.1037 & 0.0733 & 0.0574 & 0.0499 \\ 
  3 & 0.3133 & 0.3000 & 0.2759 & 0.2686 \\ 
  2 & 0.0418 & 0.0461 & 0.0377 & 0.0443 \\ 
  1 & 0.0000 & 0.0000 & 0.0000 & 0.0000 \\ 
  \bottomrule
\end{tabular}
\end{table}

@@

@@

>>>>

\presentaddress{215 Glenbrook Road, Unit 4120
Storrs, Connecticut 06269-4120}

@@

\abstract[Abstract]{The Kolmogorov--Smirnov (KS) test is a widely used statistical test that
assesses the conformity of a sample to a specified distribution. Its efficacy,
however, diminishes with serially dependent data and when parameters
within the hypothesized distribution are unknown. For independent data,
parametric and nonparametric bootstrap procedures are available to adjust for
estimated parameters. For serially dependent stationary data, parametric
bootstrap has been developed with a working serial dependence structure. A
counterpart for the nonparametric bootstrap approach, which needs a bias
correction, has not been studied. Addressing this gap, our study introduces a
bias correction method employing a nonparametric block bootstrap, which
approximates the distribution of the KS statistic accounting for unspecified
serial dependence and unspecified parameters. We assess its effectiveness
through simulations, scrutinizing both its size and power. The practicality of
our method is further illustrated with an examination of stock returns from the 
S\&P 500 index, showcasing its utility in real-world
applications.}

@@

First, let us review how the KS statistic is computed for an independent
sample with fitted parameters. Let $\hat\theta_n$ denote the parametrically
fitted parameters, which can be obtained from any consistent estimator with
asymptotic normality properties.  Let $F_n$ be the empirical distribution
function based on $X_1,...,X_n$.
Define 
\begin{equation*}
Y_n(x; \hat\theta_n) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n)).
\end{equation*}
Then, the one-sample KS goodness of fit statistic is 
\begin{equation*}
T_n := \sup_x|Y_n(x; \hat\theta_n)|.
\end{equation*}

@@

\eds{Please check consistency with how you refer to $F$.  In 
Equation~\eqref{eq:ks_standard}, it is $F(x; \theta_0)$ where the data and 
parameter arguments are separated by a semicolon.  At the beginning of 
Section~\ref{sec:methods}, it is $F(\cdot \mid \theta)$, with the vertical bar
separating the data argument from the parameter argument (and no 0 subscript
either).   Then in this first 
subsection it is $F(x; \hat\theta_n)$ with a semicolon separating the two 
arguments.  Then immediately above its use is mixed with $F(x)$ without a 
parameter argument (implying it is the true parameter $\theta$). This continues
throughout the document. I suggest either using consistent notation throughout, 
or explicitly defining any shortened/simplified notation at its first use.}

When $\{X_t: t = 1, \ldots, n\}$ are further serially dependent, the statistic
$T_n$ still provides a reasonable metric for deviation from the null
hypothesis. Nonetheless, the asymptotic distribution of $T_n$ cannot be fixed
even with the bias correction of \citet{babu2004goodness}, because the
correction requires an independent sample.

@@

In summary, the procedure of the nonparametric bootstrap KS test for independent
sample is 
summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
\begin{enumerate}
\item
  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying basic bootstrap 
  on the original sample as
  defined previously.
\item
  Fit $F_\theta$ to $X^{(b)}_1,...,X^{(b)}_n$ and obtain estimate 
	$\hat\theta^{(b)}_n$ of $\theta$.  
	\eds{$F_\theta$ has not yet been defined.}
\item
  Obtain the empirical distribution function $F^{(b)}_n$ of
  $X^{(b)}_1,...,X^{(b)}_n$. 
\item
  Calculate bootstrap KS statistic
  \[
    T^{(b)}_n = \sup_x | \sqrt{n}\left(F^{(b)}_n(x) 
    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) |.
  \]
  where 
  $B_{n}(x) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is the known
  bias term.
\end{enumerate}

@@

\eds{Do we not define $Y^{(b)}_n(x)$ in terms of the $E_n(\cdot)$'s instead of 
the $E(\cdot)$ above and below?}

@@

These distributions
were chosen to compare results on normal and non-normal
error structures. The specific parameters were chosen because the distributions 
are very similar and their
first two moments are the same. 
For the purposes of 
evaluating if the test holds it size, when $X_t \sim N(8, 8)$, we tested that the 
marginal distribution is from the
Normal family, or 
$X_t \sim N(\cdot \mid \mu, \sigma^2), \quad t = 1, \ldots, n$
for some unspecified $\mu$ and $\sigma$. When $X_t \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is from the Gamma family,
or
$X_t \sim \Gamma(\cdot \mid \alpha, \beta), \quad t = 1, \ldots, n$.
for some unspecified $\alpha$ and $\beta$.
\eds{Vertical bar vs semicolon to separate data and parameter arguments.}
For the block
bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
For each setting for $F$, $\tau$, and $n$, we replicate the method 1000 times 
to get the distribution of the p-values $p_r$
for the test when applied to samples from the same data generating process.
\eds{I assume $r$ is for replicate?  Please define and include how many 
total replicates you are using.}

\begin{figure}[tbp]
  \centering
  \includegraphics[width = .9\textwidth]{figures/normal}
  \includegraphics[width = .9\textwidth]{figures/gamma}
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal normal distribution with true data generating distribution
    being $N(8,8)$ (upper) and marginal gamma distribution with true data
    generating distribution $\Gamma(8,1)$ (lower).}
  \label{fig:qq}
\end{figure}

Figure~\ref{fig:qq} shows the Quantile-Quantile (Q-Q)
plots of the p-values testing the marginal distribution of the stationary time
series generated from the null hypothesis, created with R packages
\textsl{qqplotr} and \textsl{ggplot2} \citep{qqplotr, ggplot2}. If the
distribution of the p-values is uniform, the points will be aligned with the
diagonal line. The plots suggest that the extent to which the p-values are
uniformly distributed is dependent on the sample size and the level of serial 
dependence.
A small sample size like $n = 100$ or $200$ seems adequate when Kendall's
$\tau$ is lower than 0.25. For Kendall's $\tau \geq 0.5$, a sample larger than
$n = 200$ seems necessary for the p-values to be normally 
\eds{uniformly?} distributed. For
Kendall's $\tau \geq 0.75$, a sample larger than $n = 800$ appears to be 
necessary, as the p-values are not aligned with the line in any of the Q-Q 
plots. This
is not necessarily a cause for concern, as (for normal margins)
a Kendall's $\tau$ corresponds to
a $\phi$ of 0.924, which is very high.
Additionally, positive serial dependence appears to misalign the distribution
of the p-values more so than negative serial dependences of the same strength.
Results are very similar for normal and gamma margins.

\begin{table}[tbp]
\centering
\caption{Rejection rates for test that sample follows its true
                    distribution family for
                   different values of AR(1) coefficient and for different 
                   significance levels.
		\eds{Not sure if it will help presentation or interpretation, but you could
	consider presenting the values inside the table as estimated size/true size}}
\label{table:size}
\begin{tabular}{lllrrrrrrr}
  \toprule
$F(\cdot; \theta)$ & $n$ & $\alpha$ & $\tau = -0.75$ & $\tau = -0.5$ & $\tau = -0.25$ 
& $\tau = 0$ & $\tau = 0.25$ & $\tau = 0.5$ & $\tau = 0.75$ \\ 
  \midrule
{$N(8,8)$} & {100} & 0.01 & 0.052 & 0.013& 0.007 & 0.011 & 0.009 & 0.013 & 0.058 \\ 
& & 0.05 & 0.138 & 0.061 & 0.038 & 0.059 & 0.054 & 0.083 & 0.178 \\ 
& & 0.10 & 0.238 & 0.125 & 0.089 & 0.124 & 0.102 & 0.152 & 0.272 \\ 
& {200} & 0.01 & 0.043 & 0.009 & 0.006 & 0.017 & 0.011 & 0.018 & 0.062 \\ 
& & 0.05 & 0.130 & 0.058 & 0.041 & 0.051 & 0.053 & 0.061 & 0.175 \\ 
& & 0.10 & 0.202 & 0.120 & 0.101 & 0.107 & 0.110 & 0.125 & 0.266 \\ 
& {400} & 0.01 & 0.037 & 0.011 & 0.009 & 0.014 & 0.013 & 0.009 & 0.043 \\ 
& & 0.05 & 0.109 & 0.047 & 0.052 & 0.061 & 0.044 & 0.064 & 0.133 \\ 
& & 0.10 & 0.174 & 0.099 & 0.098 & 0.108 & 0.099 & 0.123 & 0.212 \\ 
& {800} & 0.01 & 0.023 & 0.011 & 0.008 & 0.011 & 0.011 & 0.011 & 0.038 \\ 
& & 0.05 & 0.088 & 0.043 & 0.040 & 0.055 & 0.042 & 0.053 & 0.125 \\ 
& & 0.10 & 0.166 & 0.097 & 0.095 & 0.102 & 0.107 & 0.109 & 0.196 \\ [1ex]
{$\Gamma(8,1)$} & {100} & 0.01 & 0.056 & 0.014 & 0.006 & 0.011 & 0.009 & 0.015 & 0.063 \\
  & & 0.05 & 0.144 & 0.063 & 0.037 & 0.059 & 0.053 & 0.083 & 0.180 \\ 
  & & 0.10 & 0.239 & 0.125 & 0.092 & 0.126 & 0.103 & 0.150 & 0.273 \\ 
  & {200} & 0.01 & 0.045 & 0.012 & 0.005 & 0.017 & 0.012 & 0.020 & 0.066 \\ 
  & & 0.05 & 0.127 & 0.058 & 0.045 & 0.052 & 0.054 & 0.056 & 0.173 \\ 
  & & 0.10 & 0.204 & 0.123 & 0.103 & 0.106 & 0.108 & 0.129 & 0.263 \\ 
  & {400} & 0.01 & 0.038 & 0.012 & 0.010 & 0.014 & 0.010 & 0.010 & 0.045 \\ 
  & & 0.05 & 0.106 & 0.049 & 0.051 & 0.062 & 0.042 & 0.063 & 0.128 \\ 
  & & 0.10 & 0.175 & 0.097 & 0.098 & 0.107 & 0.100 & 0.122 & 0.211 \\ 
  & {800} & 0.01 & 0.024 & 0.011 & 0.007 & 0.011 & 0.011 & 0.010 & 0.039 \\ 
  & & 0.05 & 0.089 & 0.043 & 0.041 & 0.055 & 0.044 & 0.051 & 0.121 \\ 
  & & 0.10 & 0.169 & 0.096 & 0.094 & 0.100 & 0.109 & 0.110 & 0.194 \\ 
   \bottomrule
\end{tabular}
\end{table}

For a closer scrutiny on whether the test holds its size at commonly used
significance levels 0.01, 0.05, and 0.10, Table~\ref{table:size}
summarizes the empirical sizes of the tests based on 1000 replicates.
\eds{Number of replicates needs to be stated earlier.  Also, is 1000 enough
to truly evaluate whether size is good at the 0.01 level?}
The agreement between the empirical sizes and the nominal size
improves as sample size increases, as expected. For $\tau = -0.75$
and $\tau = 0.75$, a sample size as large as 800 is still not sufficient for the
agreement to be reached. For weaker dependence levels, our approach is working
for $-0.25 < \tau < 0.25$ for $n = 100$. However, a larger sample size seems 
necessary, greater than 400 perhaps, for $\tau$ as strong as $0.5$. To 
summarize, for weaker dependence, our method works without need for a 
particularly large sample size, whereas for moderate dependence, a larger sample
size is required. For practical situations with a $\tau$ of magnitude 0.5 or
lower, it is still reasonable to recommend our method with $n \ge 400$.

\subsection{Power}
The power of the proposed test is investigated with data generated from
distributions that are not in the hypothesized distribution family. 
We generated the same scheme of time series as we did in the size investigation,
but tested that the time series was from the other distribution.
Because the support of $N(8, 8)$ is
$(-\infty, \infty)$, but the support of $\Gamma(8, 1)$ is $(0, \infty)$, we used
the \textsl{truncdist} package \citep{truncdist} to truncate the series at 
values less than or equal to 0 when testing that the $N(8, 8)$ sample was
from $\Gamma(8, 1)$. For each setting for $F$, $\tau$, and $n$, we replicate the 
method $1000$ times 
to obtain a p-value $p_r$ for each $r \in \{1, \ldots, 1000\}$.
The empirical rejection rates were obtained at a nominal significance level 0.05.
Additionally, we constructed 95\% confidence intervals the actual rejection
rejection rate.

@@

Figure~\ref{fig:rr} displays the empirical power curve of the test at
significance level 0.05 as the lag-1 Kendall's~$\tau$ increases from
$-0.5$ to $0.5$. We omitted -0.75 and 0.75 from this study because we already 
found that our method doesn't work under the null hypothesis for such high
dependence levels under the sample sizes considered. It appears that the 
rejection rate seems to decline as $\tau$
increases. Rejection rates are negatively affected by positive serial 
dependence, but they do not seem to be affected by negative serial dependencies
of the same strength.
Using $n \geq 400$ seems to be good enough
if $\tau < 0.5$, but using a $n \geq 800$ will result in 
rejection rates close to 1 for $0.5 < \tau < 0.5$.
Results for $n \geq 400$
do not appear to be to different when comparing gamma and normal 
margins, indicating that the method is robust to the marginal distribution.
The rejection rates for $n = 800$ are very 
high (almost 1), indicating that under $H_A$, the test is very powerful 
when a large enough sample size is used.

@@

Using the \textsl{tseries} package \citep{tseries}, 
we gathered daily closing prices for the S\&P 500 index from January 1st, 2020
to December 31st, 2023. Daily returns were obtained by taking the difference in
the logarithm of the closing prices. 
It is known as stylized facts that daily return series often exhibit nonlinear
dependence and unconditional heavy tails \citep[e.g.,][]{ryden1998stylized,
  cont2001empirical}. The lag-1 Kendall's $\tau$ of the series is
about $-0.0298$, indicating a fairly weak serial linear correlation, but
certainly not meaning absence of serial dependence.
Using our method, we tested that the daily returns are normally
distributed and Student's $t$ distributed 
with degrees of freedom $\nu \in \{30, 20, 10, 5, 4, 3, 2, 1\}$
with the proposed nonparametric block bootstrap (NPBB) method.
\eds{Introduce this acronym earlier (as early as in the intro), and use it 
throughout the ms.}
For comparison, we tested the same hypotheses using 1) the
semiparametric bootstrap (SPB) method of \citet{zeimbekakis2022misuses},
which accounts for both serial dependence and unspecified parameters;
2) nonparametric bootstrap (NPB) bias correction method of
\citet{babu2004goodness}; and and 3) the parametric bootstrap (PB) method shown
by \citet{zeimbekakis2022misuses}. The latter of the two methods discard the
serial dependence. In all methods, we used $B = 10,000$ bootstrap replicates.
The p-values for these tests are summarized in 
Table~\ref{table:SP5004}.

\begin{table}[ht]
\centering
\caption{P-values for 4 years of S\&P 500 stock return 
  data using different durations
  and different degrees of freedom for Student's $t$ distribution.
	\eds{how are ``different durations'' reflected in this table?}
  NPBB: nonparametric block bootstrap;
  SPB: semiparametric bootstrap;
  NPB: nonparametric bootstrap;
  PB: parametric bootstrap.} 
\label{table:SP5004}
\begin{tabular}{ccccc}
  \toprule
$\nu$ & NPBB & SPB & NPB & PB\\ 
  \midrule
$\infty$ & 0.0001 & 0.0000 & 0.0000 & 0.0000 \\ 
  30 & 0.0019 & 0.0000 & 0.0000 & 0.0000 \\ 
  20 & 0.0027 & 0.0000 & 0.0000 & 0.0000 \\ 
  10 & 0.0125 & 0.0002 & 0.0003 & 0.0003 \\ 
  5 & 0.0610 & 0.0192 & 0.0222 & 0.0141 \\ 
  4 & 0.1037 & 0.0733 & 0.0574 & 0.0499 \\ 
  3 & 0.3133 & 0.3000 & 0.2759 & 0.2686 \\ 
  2 & 0.0418 & 0.0461 & 0.0377 & 0.0443 \\ 
  1 & 0.0000 & 0.0000 & 0.0000 & 0.0000 \\ 
  \bottomrule
\end{tabular}
\end{table}

@@

\eds{I think it would be better to show in simulation first (perhaps 
in supplemental materials if we are concerned with paper length) that the other
methods are not valid or unreliable under this setting, and then 
further discredit those results here in the real data analysis.
(I would expect a reviewer to ask for this comparison anyway.)}

@@

\eds{can Mathew's AJUR paper be cited somewhere in this document?}
